Thoughts on resubmission within ARC1

### 2009-03-12 doc/client/client_technical.tex
Updating resubmission part

\documentclass{book}
%\documentclass{article}           %for shorter notes
\usepackage{graphicx}              %for PNG images (pdflatex)
%\usepackage{graphics}              %for EPS images (latex)
\usepackage[linkbordercolor={1.0 1.0 0.0}]{hyperref}  %for \url tag
\usepackage{color}                 %for defining custom colors
\usepackage{framed}                %for shaded and framed paragraphs
\usepackage{textcomp}              %for various symbols, e.g. Registered Mark
\usepackage{geometry}              %for defining page size
\usepackage{longtable}             %for breaking tables
%
\geometry{verbose,a4paper,tmargin=2.5cm,bmargin=2.5cm,lmargin=2.5cm,rmargin=2cm}
\hypersetup{
  pdfauthor = {KnorARC collaboration},
  pdftitle = {libarcclient},
  pdfsubject = {A Client Library for ARC},
  pdfkeywords = {ARC,client,library},
  pdfcreator = {PDFLaTeX with hyperref package},
  pdfproducer = {PDFLaTeX}
}
%
\bibliographystyle{IEEEtran}       %a nice bibliography style
%
\def\efill{\hfill\nopagebreak}%
\hyphenation{Nordu-Grid}
\setlength{\parindent}{0cm}
\setlength{\FrameRule}{1pt}
\setlength{\FrameSep}{8pt}
\addtolength{\parskip}{5pt}
\renewcommand{\thefootnote}{\fnsymbol{footnote}}
\renewcommand{\arraystretch}{1.3}
\newcommand{\dothis}{\colorbox{shadecolor}}
\newcommand{\globus}{Globus Toolkit\textsuperscript{\textregistered}~2~}
\newcommand{\GT}{Globus Toolkit\textsuperscript{\textregistered}}
\newcommand{\ngdl}{\url{http://ftp.nordugrid.org/download}~}
\newcommand{\libarcclient}{libarcclient}
\newcommand{\ACC}{\texttt{ACC}}
\newcommand{\ACCConfig}{\texttt{ACCConfig}}
\newcommand{\Config}{\texttt{Config}}
\newcommand{\Broker}{\texttt{Broker}}
\newcommand{\RandomBroker}{\texttt{RandomBroker}}
\newcommand{\FastestCPUBroker}{\texttt{FastestCPUBroker}}
\newcommand{\FastestQueueBroker}{\texttt{FastestQueueBroker}}
\newcommand{\PythonBroker}{\texttt{PythonBroker}}
\newcommand{\DataBroker}{\texttt{DataBroker}}
\newcommand{\ClientInterface}{\texttt{ClientInterface}}
\newcommand{\ClientTCP}{\texttt{ClientTCP}}
\newcommand{\ClientHTTP}{\texttt{ClientHTTP}}
\newcommand{\ClientSOAP}{\texttt{ClientSOAP}}
\newcommand{\ExecutionTarget}{\texttt{ExecutionTarget}}
\newcommand{\Job}{\texttt{Job}}
\newcommand{\JobController}{\texttt{JobController}}
\newcommand{\JobDescription}{\texttt{JobDescription}}
\newcommand{\JobSupervisor}{\texttt{JobSupervisor}}
\newcommand{\Loader}{\texttt{Loader}}
\newcommand{\Logger}{\texttt{Logger}}
\newcommand{\TargetGenerator}{\texttt{TargetGenerator}}
\newcommand{\TargetRetriever}{\texttt{TargetRetriever}}
\newcommand{\Submitter}{\texttt{Submitter}}
\newcommand{\URL}{\texttt{URL}}
\newcommand{\UserConfig}{\texttt{UserConfig}}
\newcommand{\XML}{\texttt{XML}}
\newcommand{\XMLNode}{\texttt{XMLNode}}
\definecolor{shadecolor}{rgb}{1,1,0.6}
\definecolor{salmon}{rgb}{1,0.9,1}
\definecolor{bordeaux}{rgb}{0.75,0.,0.}
\definecolor{cyan}{rgb}{0,1,1}
%
%----- DON'T CHANGE HEADER MATTER
\begin{document}
\def\today{\number\day/\number\month/\number\year}

@@

Once a job is submitted job related information (job identification
string, cluster etc) is stored in a local XML file which stores this 
information for all active jobs. This file may contain jobs running on
completely different grid flavours, and thus job management should be
handled using plugins similar to resource discovery and job
submission. The job managing plugin is called the {\JobController} and
it is supported by the {\JobSupervisor} and {\Job} classes.

@@

The {\Broker} inherits from the {\ACC} base class in order to be loadable by the ARC \texttt{Loader}. It is the base class of the 
specialized {\Broker} and it implements the method for reducing a list of resources found by resource discovery (the list of 
{\ExecutionTarget}s residing witin the {\TargetGenerator}) to a list of resources capable of running a certain job:

@@

The {\texttt PreFilterTargets} method compares every hardware and software requirement given in the job description against the 
computing resource (cluster) specifications stored in the {\ExecutionTarget}. If the{\ExecutionTarget} doesn't fulfill 
the requirements imposed by the job description, or it is impossible to carry out the matchmaking due to incomplete information 
published by the computing resource, the {\ExecutionTarget} will be removed from the list of possible targets. A detailed overview 
of the matchmaking between {\JobDescription} and {\ExecutionTarget} attributes is given in Appendix~\ref{sec:broker-mapping}.

@@

Once the job description language required by the {\ExecutionTarget} chosen 
for job submission is known the parsed and (if needed) translated job description 
can be retrieved through the {\texttt GetProduct} funcion as shown below:

@@

If the inner representation is empty or the source job descrition is not
valid, then the {\texttt GetProduct} output is empty too and the method 
returns with false. When the product format is the same as the source format 
and not XRSL, than the product string is set to the source string. The XRSL 
output is always generated from the inner representation, as it includes 
automatic job description modifications similar to those of the production 
ARC client. If the product format differs from the source format the 
{\texttt GetProduct} method calls upon the \texttt{JobDescriptionOrderer} 
class to carry out the translation.

The translation of a job description basically means a syntactical transformation 
of the job description from one language to another. Thus the {\JobDescription}
class can do nothing in those cases where there is not enough data is available 
to assemble a given attribute or when information can be lost because the received 
attribute has no equivalent in the output language. In these events the {\texttt GetProduct} 
method returns with a false and an empty product stringt. For limitations in the translation
see Section~\ref{sec:jobinnerrepresentation}.

@@

@@

The steps above completes the initialization of the {\JobController}
which is now ready for handling jobs. The public functions of the
{\JobController} offer to get (download), clean, cancel, etc one or
more jobs and uses the private specializations for issuing the
command. Here exemplified by the \texttt{Stat} command:

@@

@@

\begin{shaded}
\begin{verbatim}
const std::string& JobListFile() const;
const XMLNode& ConfTree() const;
bool ApplySecurity(XMLNode& ccfg) const;
\end{verbatim}
\end{shaded}

@@

@@

\begin{enumerate}
\item{{\ExecutionTarget}s not publishing WaitingJobs, TotalSlots and FreeSlots are removed from the list of possible targets 
as it is impossible to determine their queue length and perform load balancing.}
\item{The {\ExecutionTarget}s are ranked according to their queue length relative to the number of slots/CPUs. Zero queue 
{\ExecutionTarget}s is ranked top.}
\item{If more than one {\ExecutionTarget} has zero queue the targets are randomly reshuffled based upon how many free slots 
they have. E.g. if two {\ExecutionTarget}s have zero queue and they have 90 and 10 free slots respectively, then the first
{\ExecutionTarget} has a 90\% propability of becoming the top ranked cluster.}
\end{enumerate}

@@

\begin{enumerate}
\item{\texttt{arcstat} - for computing resource or grid job status
  queries.}
\item{\texttt{arcsub} - for grid job submission}
\item{\texttt{arcget} - for downloading output of finished, cancelled
  or failed grid jobs.}
\item{\texttt{arckill} - for terminating grid jobs.}
\item{\texttt{arcclean} - for removing a grid job's session directory
  including all contents}
\item{\texttt{arccat} - for performing the \texttt{cat} command to a
  running grid job's std out or std error file.}
\end{enumerate}

>>>>

\documentclass{book}
%\documentclass{article}           %for shorter notes
\usepackage{graphicx}              %for PNG images (pdflatex)
%\usepackage{graphics}              %for EPS images (latex)
\usepackage[linkbordercolor={1.0 1.0 0.0}]{hyperref}  %for \url tag
\usepackage{color}                 %for defining custom colors
\usepackage{framed}                %for shaded and framed paragraphs
\usepackage{textcomp}              %for various symbols, e.g. Registered Mark
\usepackage{geometry}              %for defining page size
\usepackage{longtable}             %for breaking tables
%
\geometry{verbose,a4paper,tmargin=2.5cm,bmargin=2.5cm,lmargin=2.5cm,rmargin=2cm}
\hypersetup{
  pdfauthor = {KnorARC collaboration},
  pdftitle = {libarcclient},
  pdfsubject = {A Client Library for ARC},
  pdfkeywords = {ARC,client,library},
  pdfcreator = {PDFLaTeX with hyperref package},
  pdfproducer = {PDFLaTeX}
}
%
\bibliographystyle{IEEEtran}       %a nice bibliography style
%
\def\efill{\hfill\nopagebreak}%
\hyphenation{Nordu-Grid}
\setlength{\parindent}{0cm}
\setlength{\FrameRule}{1pt}
\setlength{\FrameSep}{8pt}
\addtolength{\parskip}{5pt}
\renewcommand{\thefootnote}{\fnsymbol{footnote}}
\renewcommand{\arraystretch}{1.3}
\newcommand{\dothis}{\colorbox{shadecolor}}
\newcommand{\globus}{Globus Toolkit\textsuperscript{\textregistered}~2~}
\newcommand{\GT}{Globus Toolkit\textsuperscript{\textregistered}}
\newcommand{\ngdl}{\url{http://ftp.nordugrid.org/download}~}
\newcommand{\libarcclient}{libarcclient}
\newcommand{\ACC}{\texttt{ACC}}
\newcommand{\ACCConfig}{\texttt{ACCConfig}}
\newcommand{\Config}{\texttt{Config}}
\newcommand{\Broker}{\texttt{Broker}}
\newcommand{\RandomBroker}{\texttt{RandomBroker}}
\newcommand{\FastestCPUBroker}{\texttt{FastestCPUBroker}}
\newcommand{\FastestQueueBroker}{\texttt{FastestQueueBroker}}
\newcommand{\PythonBroker}{\texttt{PythonBroker}}
\newcommand{\DataBroker}{\texttt{DataBroker}}
\newcommand{\ClientInterface}{\texttt{ClientInterface}}
\newcommand{\ClientTCP}{\texttt{ClientTCP}}
\newcommand{\ClientHTTP}{\texttt{ClientHTTP}}
\newcommand{\ClientSOAP}{\texttt{ClientSOAP}}
\newcommand{\ExecutionTarget}{\texttt{ExecutionTarget}}
\newcommand{\Job}{\texttt{Job}}
\newcommand{\JobController}{\texttt{JobController}}
\newcommand{\JobDescription}{\texttt{JobDescription}}
\newcommand{\JobSupervisor}{\texttt{JobSupervisor}}
\newcommand{\Loader}{\texttt{Loader}}
\newcommand{\Logger}{\texttt{Logger}}
\newcommand{\TargetGenerator}{\texttt{TargetGenerator}}
\newcommand{\TargetRetriever}{\texttt{TargetRetriever}}
\newcommand{\Sandbox}{\texttt{Sandbox}}
\newcommand{\Submitter}{\texttt{Submitter}}
\newcommand{\URL}{\texttt{URL}}
\newcommand{\UserConfig}{\texttt{UserConfig}}
\newcommand{\XML}{\texttt{XML}}
\newcommand{\XMLNode}{\texttt{XMLNode}}
\definecolor{shadecolor}{rgb}{1,1,0.6}
\definecolor{salmon}{rgb}{1,0.9,1}
\definecolor{bordeaux}{rgb}{0.75,0.,0.}
\definecolor{cyan}{rgb}{0,1,1}
%
%----- DON'T CHANGE HEADER MATTER
\begin{document}
\def\today{\number\day/\number\month/\number\year}

@@

Once a job is submitted job related information (job identification
string, cluster etc.) is stored in a local XML file which stores this 
information for all active jobs. This file may contain jobs running on
completely different grid flavours, and thus job management should be
handled using plugins similar to resource discovery and job
submission. The job managing plugin is called the {\JobController} and
it is supported by the {\JobSupervisor} and {\Job} classes.

@@

The {\Broker} inherits from the {\ACC} base class in order to be loadable by the ARC \texttt{Loader}. It is the base class of the 
specialized {\Broker} and it implements the method for reducing a list of resources found by resource discovery (the list of 
{\ExecutionTarget}s residing within the {\TargetGenerator}) to a list of resources capable of running a certain job:

@@

The {\texttt PreFilterTargets} method compares every hardware and software requirement given in the job description against the 
computing resource (cluster) specifications stored in the {\ExecutionTarget}. If the{\ExecutionTarget} doesn't fulfil 
the requirements imposed by the job description, or it is impossible to carry out the matchmaking due to incomplete information 
published by the computing resource, the {\ExecutionTarget} will be removed from the list of possible targets. A detailed overview 
of the matchmaking between {\JobDescription} and {\ExecutionTarget} attributes is given in Appendix~\ref{sec:broker-mapping}.

@@

Once the job description language required by the {\ExecutionTarget} chosen 
for job submission is known the parsed and (if needed) translated job description 
can be retrieved through the {\texttt GetProduct} function as shown below:

@@

If the inner representation is empty or the source job description is not
valid, then the {\texttt GetProduct} output is empty too and the method 
returns with false.  In order to obtain the automatic job description 
modifications similar to those of the production ARC client, the 
{\texttt GetProduct} output is always generated from the internal 
representation using the \texttt{JobDescriptionOrderer} class to carry 
out the translation. The original source string can be regained by
calling the \texttt{getSourceString} method:

\begin{shaded}
\begin{verbatim}
bool getSourceString(std::string source) const;
\end{verbatim}
\end{shaded}

The translation of a job description basically means a syntactical transformation 
of the job description from one language to another. Thus the {\JobDescription}
class can do nothing in those cases where there is not enough data is available 
to assemble a given attribute or when information can be lost because the received 
attribute has no equivalent in the output language. In these events the {\texttt GetProduct} 
method returns with a false and an empty product string. For limitations in the translation
see Section~\ref{sec:jobinnerrepresentation}.

@@

In case of job resubmission the internal representation will contain a list of 
the jobid's of the previous jobs. This element will only be parsed to the 
actually job description in case JSDL-POSIX output is requested. A new URL 
can be added to the list of old jobid's by using the method:

\begin{shaded}
\begin{verbatim}
bool addOldJobID(const URL& oldjobid);
\end{verbatim}
\end{shaded}

@@

The steps above completes the initialization of the {\JobController}
which is now ready for handling jobs. The public functions of the
{\JobController} offer to get (download), clean, cancel, etc. one or
more jobs and uses the private specializations for issuing the
command. Here exemplified by the \texttt{Stat} command:

@@

The other public functions of the {\JobController} class are:
The \texttt{Get} which is used to download jobs
\begin{shaded}
\begin{verbatim}
bool Get(const std::list<std::string>& status, const std::string& downloaddir,
         const bool keep, const int timeout);
\end{verbatim}
\end{shaded}
\begin{shaded}
\begin{verbatim}
bool Kill(const std::list<std::string>& status, const bool keep, const int timeout);
\end{verbatim}
\end{shaded}
\begin{shaded}
\begin{verbatim}
bool Clean(const std::list<std::string>& status, const bool force, const int timeout);
\end{verbatim}
\end{shaded}
\begin{shaded}
\begin{verbatim}
bool Cat(const std::list<std::string>& status, const std::string& whichfile, 
         const int timeout);
\end{verbatim}
\end{shaded}
\begin{shaded}
\begin{verbatim}
bool RemoveJobs(const std::list<URL>& jobids);
\end{verbatim}
\end{shaded}
\begin{shaded}
\begin{verbatim}
std::list<std::string> GetDownloadFiles(const URL& dir);
\end{verbatim}
\end{shaded}
\begin{shaded}
\begin{verbatim}
bool CopyFile(const URL& src, const URL& dst);
\end{verbatim}
\end{shaded}
The \texttt{GetJobDescriptions} method 
\begin{shaded}
\begin{verbatim}
std::list<Job> GetJobDescriptions(const std::list<std::string>& status, 
                                  const bool getlocal, const int timeout);
\end{verbatim}
\end{shaded}
which is used to get the job descriptions of {\Job}s in the \texttt{JobStore} 
with the specified status'. In case \texttt{getlocal} is true the job description 
will first be searched for the users local XML file. If a local copy of 
the job description is found the checksum of the local input files will be 
computed and compared with the ones listed in the users local XML file. If 
all checksums match the job description is returned.\\
In case \texttt{getlocal} is false or the retrieval of the local job description 
fails the job description will be tried retrieved from the cluster. This has 
currently only been implemented for ARC(both generations) clusters. Note 
that the job descriptions retried from a cluster might will most likely have 
been changed since the submission either by the cluster\footnote{For both 
generations of ARC it is possible to recover the initial job description send 
to the cluster. However modifications can still have been made to the 
job description before sending it to the cluster.} or by the submission 
client. Therefore the only way of retrieving the original job description is 
through the users local XML file.\\
The \texttt{GetJobDescriptions} returns a list of the  {\Job}s where job description 
have been found. The found job descriptions are kept in the 
{\Job}.\texttt{JobDescription} attribute.

@@

\begin{shaded}
\begin{verbatim}
const std::string& JobListFile() const;
const & ConfTree() const;
bool ApplySecurity(XMLNode& ccfg) const;
\end{verbatim}
\end{shaded}

@@

\subsection{{\Sandbox}}
The {\Sandbox} class, consisting of the two methods \texttt{Add} and 
\texttt{GetCkSum}, have been created to assure a reliable resubmission 
of jobs. 
\begin{shaded}
\begin{verbatim}
static bool Add(JobDescription& jobdesc, XMLNode& info);
static std::string GetCksum(const std::string& file);
\end{verbatim}
\end{shaded}
The \texttt{Add} method  adds the job description and the checksum of 
the local input files to a {\XMLNode}. Currently this {\XMLNode} is the one 
stored in the user's local XML file upon job submission. The job 
description which is stored is the initial job description before any 
parsing has been performed. To calculate the checksum of the input 
files the \texttt{GetCkSum} method is used. The \texttt{GetCkSum} 
method returns the MD5 checksum of a given file

@@

\begin{enumerate}
\item{{\ExecutionTarget}s not publishing WaitingJobs, TotalSlots and FreeSlots are removed from the list of possible targets 
as it is impossible to determine their queue length and perform load balancing.}
\item{The {\ExecutionTarget}s are ranked according to their queue length relative to the number of slots/CPUs. Zero queue 
{\ExecutionTarget}s is ranked top.}
\item{If more than one {\ExecutionTarget} has zero queue the targets are randomly reshuffled based upon how many free slots 
they have. E.g. if two {\ExecutionTarget}s have zero queue and they have 90 and 10 free slots respectively, then the first
{\ExecutionTarget} has a 90\% probability of becoming the top ranked cluster.}
\end{enumerate}

@@

\begin{enumerate}
\item{\texttt{arcstat} - for computing resource or grid job status
  queries.}
\item{\texttt{arcsub} - for grid job submission}
\item{\texttt{arcget} - for downloading output of finished, cancelled
  or failed grid jobs.}
\item{\texttt{arckill} - for terminating grid jobs.}
\item{\texttt{arcclean} - for removing a grid job's session directory
  including all contents}
\item{\texttt{arccat} - for performing the \texttt{cat} command to a
  running grid job's std out or std error file.}
\item{\texttt{arcsync} - for synchronising the information in the user's
  local XML file about active jobs.}
\item{\texttt{arcresub} - for redoing an entire job on the same or a new
  computing resource.}
\item{\texttt{arcmigrate} - for moving a queuing job from an ARC1 
  computing resource to another.}
\end{enumerate}
